Placeholder

### 2021-02-06 Paper_Histograms.Rmd
Merged all the positive diagnosis/positive control tibbles together

>>>>

dat.retro_positive_diagnosis_by_sample <- left_join(dat.retro_positive_diagnosis_by_sample,
                                                    dat.retro_ED_by_sample,
                                                    by = "Sample_plot")

dat.retro_positive_diagnosis_by_sample <- left_join(dat.retro_positive_diagnosis_by_sample,
                                                    dat.retro_OCD_by_sample,
                                                    by = "Sample_plot")

dat.retro_positive_diagnosis_by_sample <- left_join(dat.retro_positive_diagnosis_by_sample,
                                                    dat.retro_psychosis_by_sample,
                                                    by = "Sample_plot")

dat.retro_positive_diagnosis_by_sample <- left_join(dat.retro_positive_diagnosis_by_sample,
                                                    dat.retro_ASD_by_sample,
                                                    by = "Sample_plot")

dat.retro_positive_diagnosis_by_sample <- left_join(dat.retro_positive_diagnosis_by_sample,
                                                    dat.retro_ADHD_by_sample,
                                                    by = "Sample_plot")

dat.retro_positive_diagnosis_by_sample <- left_join(dat.retro_positive_diagnosis_by_sample,
                                                    dat.retro_PD_by_sample,
                                                    by = "Sample_plot")

dat.retro_positive_diagnosis_by_sample <- left_join(dat.retro_positive_diagnosis_by_sample,
                                                    dat.retro_BD_by_sample,
                                                    by = "Sample_plot")

dat.retro_positive_diagnosis_by_sample <- left_join(dat.retro_positive_diagnosis_by_sample,
                                                    dat.retro_PTSD_by_sample,
                                                    by = "Sample_plot")

dat.retro_positive_diagnosis_by_sample <- left_join(dat.retro_positive_diagnosis_by_sample,
                                                    dat.retro_control_by_sample,
                                                    by = "Sample_plot")
